---
title: "Sales_Reg"
author: "Author : Samarth"
date: "Date Created : 5/9/2018"
output: html_document
---

# Clear Environment
```{r}
rm(list=ls(all=TRUE))
```

# Read in the dataset 
```{r}
sale_data <- read.csv("Train.csv", header = T, na.strings = c('', ' '))
```

# Basic exploration of dataset
```{r}
str(sale_data)
summary(sale_data)
```

# Fix errors observed from basic exploration of data 
*Extra number of levels were observed in fat content column
```{r}
sale_data[which(sale_data$Item_Fat_Content == 'Low Fat'),'Item_Fat_Content'] <- 'low fat'
sale_data[which(sale_data$Item_Fat_Content == 'LF'),'Item_Fat_Content'] <- 'low fat'
sale_data[which(sale_data$Item_Fat_Content == 'reg'),'Item_Fat_Content'] <- 'Regular'
sale_data$Item_Fat_Content <- as.factor(as.character(sale_data$Item_Fat_Content))
summary(sale_data) #Levels of fat content are fixed to two levels
```

# Data Exploration Through Visualization
*Univariate Analysis
## Plot histograms of numerical atrributes
```{r}
par(mfrow = c(2,2))
hist(sale_data$Item_Weight)
hist(sale_data$Item_Visibility) #Could log Item Visibility to achieve normal distribution
hist(sale_data$Item_MRP)
hist(sale_data$Outlet_Establishment_Year)
#Target Variable
par(mfrow = c(1,1))
hist(sale_data$Item_Outlet_Sales)
```

## Plot histogram for categorical attributes (levels frequency)
```{r}
library(ggplot2)
ggplot(data = sale_data, aes(x = sale_data$Item_Fat_Content)) + geom_bar()
ggplot(data = sale_data, aes(x = sale_data$Item_Type)) + geom_bar()
ggplot(data = sale_data, aes(x = sale_data$Outlet_Size)) + geom_bar()
ggplot(data = sale_data, aes(x = sale_data$Outlet_Location_Type)) + geom_bar()
ggplot(data = sale_data, aes(x = sale_data$Outlet_Type)) + geom_bar()
```

# Bivariate Analysis
## Scatter plots of numerical attributes versus target (numeric v/s numeric)
```{r}
ggplot(data = sale_data, aes(x = sale_data$Item_Weight, y = sale_data$Item_Outlet_Sales)) + geom_point()
ggplot(data = sale_data, aes(x = sale_data$Item_Visibility, y =sale_data$Item_Outlet_Sales)) + geom_point()
ggplot(data = sale_data, aes(x = sale_data$Item_MRP, y = sale_data$Item_Outlet_Sales)) + geom_point()
ggplot(data = sale_data, aes(x = sale_data$Outlet_Establishment_Year, y = sale_data$Item_Outlet_Sales)) + geom_point()
```

## Scatter plots of numerical attributes versus target (Categorical v/s Categorical)
```{r}
ggplot(sale_data, aes(sale_data$Outlet_Type, fill = sale_data$Outlet_Size)) + geom_bar()
ggplot(sale_data, aes(sale_data$Item_Fat_Content, fill = sale_data$Outlet_Size)) + geom_bar()
ggplot(sale_data, aes(sale_data$Item_Type, fill = sale_data$Item_Fat_Content)) + geom_bar()
ggplot(sale_data, aes(sale_data$Outlet_Location_Type, fill = sale_data$Item_Type)) + geom_bar()
```








